Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-12 Paper/paper.tex
adding some nice figs to paper tex

@@

\includegraphics[width=0.65\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}

>>>>

\includegraphics[width=0.65\columnwidth]{plots/McEta2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/EtaChiBH2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/McChiBH2D_q4_mc2_25_chi0_50_snr30}\\

@@

\includegraphics[width=0.65\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}\\
\includegraphics[width=0.65\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr50}
\includegraphics[width=0.65\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr50}
\includegraphics[width=0.65\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr50}
